---
title: "data_challange"
author: "Babafela Awosile"
date: "2023-06-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



##Ceftadizime

```{r}
library(tidyverse)
library(readr)
library (moments)
library(rcompanion)


ceftadizime1 <-read.csv("ceftadizime.csv")

ceftadizime <- ceftadizime1 %>% 
  filter(Gender %in% c("Male", "Female"), Age.Group %in% c("0 to 2 Years", "3 to 12 Years", "13 to 18 Years", "19 to 64 Years", "65 to 84 Years", "85 and Over"))%>%
  select(bacteria, Country, Gender, Age.Group, Speciality, Year, Ceftazidime_mic, Ceftazidime_I, shv, tem, ctxm1, ctxm2, ctxm825, ctxm9, veb, per, ges, acc, cmy2, dha, fox, act, kpc, oxa, ndm, imp, vim)


str(ceftadizime)
summary(ceftadizime)
hist(ceftadizime$Ceftazidime_mic)

#log transformation
ceftadizime$ceftadizime_log2 <-log2(ceftadizime$Ceftazidime_mic)


ceftadizime$Year2 <- as.numeric(ceftadizime$Year)
hist(ceftadizime$ceftadizime_log2)


ceftadizime$bacteria <- as.factor(ceftadizime$bacteria)
ceftadizime$Country <- as.factor(ceftadizime$Country)
ceftadizime$Gender <- as.factor(ceftadizime$Gender)
ceftadizime$Age.Group <- as.factor(ceftadizime$Age.Group)
ceftadizime$Speciality <- as.factor(ceftadizime$Speciality)
ceftadizime$Year <- as.factor(ceftadizime$Year)
ceftadizime$shv <- as.factor(ceftadizime$shv)
ceftadizime$tem <- as.factor(ceftadizime$tem)
ceftadizime$ctxm1 <- as.factor(ceftadizime$ctxm1)
ceftadizime$ctxm2 <- as.factor(ceftadizime$ctxm2)
ceftadizime$ctxm825 <- as.factor(ceftadizime$ctxm825)
ceftadizime$ctxm9 <- as.factor(ceftadizime$ctxm9)
ceftadizime$veb <- as.factor(ceftadizime$veb)
ceftadizime$per <- as.factor(ceftadizime$per)
ceftadizime$ges <- as.factor(ceftadizime$ges)
ceftadizime$acc <- as.factor(ceftadizime$acc)
ceftadizime$cmy2 <- as.factor(ceftadizime$cmy2)
ceftadizime$dha <- as.factor(ceftadizime$dha)
ceftadizime$fox <- as.factor(ceftadizime$fox)
ceftadizime$act <- as.factor(ceftadizime$act)
ceftadizime$kpc <- as.factor(ceftadizime$kpc)
ceftadizime$oxa <- as.factor(ceftadizime$oxa)
ceftadizime$ndm <- as.factor(ceftadizime$ndm)
ceftadizime$imp <- as.factor(ceftadizime$imp)
ceftadizime$vim <- as.factor(ceftadizime$vim)



```

#ceftadizime_Simple linear regression
```{r}

library(lmtest)

ceftadi1 <- lm(ceftadizime_log2 ~ bacteria, data = ceftadizime)   
summary(ceftadi1)

ceftadi2 <- lm(ceftadizime_log2 ~ Country, data = ceftadizime)   
summary(ceftadi2)

ceftadi3 <- lm(ceftadizime_log2 ~ Gender, data = ceftadizime)   
summary(ceftadi3)

ceftadi4 <- lm(ceftadizime_log2 ~ Age.Group, data = ceftadizime)   
summary(ceftadi4)

ceftadi5 <- lm(ceftadizime_log2 ~ Speciality, data = ceftadizime)   
summary(ceftadi5)

ceftadi6 <- lm(ceftadizime_log2 ~ Year2, data = ceftadizime)   
summary(ceftadi6)

ceftadi7 <- lm(ceftadizime_log2 ~ ctxm1, data = ceftadizime)   
summary(ceftadi7)

ceftadi8 <- lm(ceftadizime_log2 ~ ctxm2, data = ceftadizime)   
summary(ceftadi8)

ceftadi9 <- lm(ceftadizime_log2 ~ ctxm825, data = ceftadizime)   
summary(ceftadi9)

ceftadi10 <- lm(ceftadizime_log2 ~ ctxm9, data = ceftadizime)   
summary(ceftadi10)

ceftadi11 <- lm(ceftadizime_log2 ~ veb, data = ceftadizime)   
summary(ceftadi11)

ceftadi12 <- lm(ceftadizime_log2 ~ per, data = ceftadizime)   
summary(ceftadi12)

ceftadi13 <- lm(ceftadizime_log2 ~ ges, data = ceftadizime)   
summary(ceftadi13)

ceftadi14 <- lm(ceftadizime_log2 ~ acc, data = ceftadizime)   
summary(ceftadi14)

ceftadi15 <- lm(ceftadizime_log2 ~ cmy2, data = ceftadizime)   
summary(ceftadi15)

ceftadi17 <- lm(ceftadizime_log2 ~ dha, data = ceftadizime)   
summary(ceftadi17)

ceftadi18 <- lm(ceftadizime_log2 ~ fox, data = ceftadizime)   
summary(ceftadi18)

ceftadi19 <- lm(ceftadizime_log2 ~ act, data = ceftadizime)   
summary(ceftadi19)

ceftadi20 <- lm(ceftadizime_log2 ~ kpc, data = ceftadizime)   
summary(ceftadi20)

ceftadi21 <- lm(ceftadizime_log2 ~ oxa, data = ceftadizime)   
summary(ceftadi21)

ceftadi22 <- lm(ceftadizime_log2 ~ ndm, data = ceftadizime)   
summary(ceftadi22)

ceftadi23 <- lm(ceftadizime_log2 ~ imp, data = ceftadizime)   
summary(ceftadi23)

ceftadi24 <- lm(ceftadizime_log2 ~ vim, data = ceftadizime)   
summary(ceftadi24)

ceftadi25 <- lm(ceftadizime_log2 ~ shv, data = ceftadizime)   
summary(ceftadi25)

ceftadi26 <- lm(ceftadizime_log2 ~ tem, data = ceftadizime)   
summary(ceftadi26)

```

#Multiple liniear Regression
```{r}
ceftadizime$bacteria <- relevel(ceftadizime$bacteria, ref = "E. coli")
ceftadizime$Gender <- relevel(ceftadizime$Gender, ref = "Male")


mceftadi1 <-lm(ceftadizime_log2 ~ Country+bacteria+Gender+Age.Group+Speciality+Year2+ctxm1+ctxm2+ctxm825+ctxm9+veb+per+ges+acc+cmy2+dha+fox+act+kpc+oxa+ndm+imp+vim+shv+tem, data = ceftadizime)


summary(mceftadi1) #Adjusted R^2 =39%

# Model diagnostics and checking
par(mfrow=c(2,2))
plot(mceftadi1)

# Extract the residuals
aov_residuals_mceftadi1 <- residuals(object = mceftadi1)
# Run Shapiro-Wilk test
#shapiro.test(x = aov_residuals_mceftadi1)

library(car)
vif(mceftadi1)


#Multicollinearity test :There was no collinearity between the variables in model 1 and 2



# Statistical test for constant variance or homoscedasticity
bptest (mceftadi1)


#p value is less than 0.05 so heterocedasticity present


```


#Robust model_Ceftadizime
```{r}
library(sandwich)
library(lmtest)
mceftadi1_robust <- coeftest(mceftadi1, vcov = vcovHC(mceftadi1, type = "HC1"))
mceftadi1_robust

confint(mceftadi1_robust)

#Log back transform was done in log Base 2 calculator
#https://www.omnicalculator.com/math/log-2

```

##Ceftraroline

```{r}
ceftraroline1 <-read.csv("ceftraroline.csv")

ceftraroline <- ceftraroline1 %>% 
  filter(Gender %in% c("Male", "Female"), Age.Group %in% c("0 to 2 Years", "3 to 12 Years", "13 to 18 Years", "19 to 64 Years", "65 to 84 Years", "85 and Over"))%>%
  select(bacteria, Country, Gender, Age.Group, Speciality, Year, Ceftaroline_mic, shv, tem, ctxm1, ctxm2, ctxm825, ctxm9, veb, per, ges, acc, cmy2, dha, fox, act, kpc, oxa, ndm, imp, vim)


str(ceftraroline)
summary(ceftraroline)
hist(ceftraroline$Ceftaroline_mic)

#log transformation
ceftraroline$ceftraroline_log2 <-log2(ceftraroline$Ceftaroline_mic)

hist(ceftraroline$ceftraroline_log2)


ceftraroline$bacteria <- as.factor(ceftraroline$bacteria)
ceftraroline$Country <- as.factor(ceftraroline$Country)
ceftraroline$Gender <- as.factor(ceftraroline$Gender)
ceftraroline$Age.Group <- as.factor(ceftraroline$Age.Group)
ceftraroline$Speciality <- as.factor(ceftraroline$Speciality)
ceftraroline$Year <- as.factor(ceftraroline$Year)
ceftraroline$shv <- as.factor(ceftraroline$shv)
ceftraroline$tem <- as.factor(ceftraroline$tem)
ceftraroline$ctxm1 <- as.factor(ceftraroline$ctxm1)
ceftraroline$ctxm2 <- as.factor(ceftraroline$ctxm2)
ceftraroline$ctxm825 <- as.factor(ceftraroline$ctxm825)
ceftraroline$ctxm9 <- as.factor(ceftraroline$ctxm9)
ceftraroline$veb <- as.factor(ceftraroline$veb)
ceftraroline$per <- as.factor(ceftraroline$per)
ceftraroline$ges <- as.factor(ceftraroline$ges)
ceftraroline$acc <- as.factor(ceftraroline$acc)
ceftraroline$cmy2 <- as.factor(ceftraroline$cmy2)
ceftraroline$dha <- as.factor(ceftraroline$dha)
ceftraroline$fox <- as.factor(ceftraroline$fox)
ceftraroline$act <- as.factor(ceftraroline$act)
ceftraroline$kpc <- as.factor(ceftraroline$kpc)
ceftraroline$oxa <- as.factor(ceftraroline$oxa)
ceftraroline$ndm <- as.factor(ceftraroline$ndm)
ceftraroline$imp <- as.factor(ceftraroline$imp)
ceftraroline$vim <- as.factor(ceftraroline$vim)

ceftraroline$Year2 <- as.numeric(ceftraroline$Year)

```

#Simple linear regression_Ceftraroline
```{r}

library(lmtest)

ceftrarol1 <- lm(ceftraroline_log2 ~ bacteria, data = ceftraroline)   
summary(ceftrarol1)

ceftrarol2 <- lm(ceftraroline_log2 ~ Country, data = ceftraroline)   
summary(ceftrarol2)

ceftrarol3 <- lm(ceftraroline_log2 ~ Gender, data = ceftraroline)   
summary(ceftrarol3)

ceftrarol4 <- lm(ceftraroline_log2 ~ Age.Group, data = ceftraroline)   
summary(ceftrarol4)

ceftrarol5 <- lm(ceftraroline_log2 ~ Speciality, data = ceftraroline)   
summary(ceftrarol5)

ceftrarol6 <- lm(ceftraroline_log2 ~ Year2, data = ceftraroline)   
summary(ceftrarol6)

ceftrarol7 <- lm(ceftraroline_log2 ~ ctxm1, data = ceftraroline)   
summary(ceftrarol7)

ceftrarol8 <- lm(ceftraroline_log2 ~ ctxm2, data = ceftraroline)   
summary(ceftrarol8)

ceftrarol9 <- lm(ceftraroline_log2 ~ ctxm825, data = ceftraroline)   
summary(ceftrarol9)

ceftrarol10 <- lm(ceftraroline_log2 ~ ctxm9, data = ceftraroline)   
summary(ceftrarol10)

ceftrarol11 <- lm(ceftraroline_log2 ~ veb, data = ceftraroline)   
summary(ceftrarol11)

ceftrarol12 <- lm(ceftraroline_log2 ~ per, data = ceftraroline)   
summary(ceftrarol12)

ceftrarol13 <- lm(ceftraroline_log2 ~ ges, data = ceftraroline)   
summary(ceftrarol13)

ceftrarol14 <- lm(ceftraroline_log2 ~ acc, data = ceftraroline)   
summary(ceftrarol14)

ceftrarol15 <- lm(ceftraroline_log2 ~ cmy2, data = ceftraroline)   
summary(ceftrarol15)

ceftrarol17 <- lm(ceftraroline_log2 ~ dha, data = ceftraroline)   
summary(ceftrarol17)

ceftrarol18 <- lm(ceftraroline_log2 ~ fox, data = ceftraroline)   
summary(ceftrarol18)

ceftrarol19 <- lm(ceftraroline_log2 ~ act, data = ceftraroline)   
summary(ceftrarol19)

ceftrarol20 <- lm(ceftraroline_log2 ~ kpc, data = ceftraroline)   
summary(ceftrarol20)

ceftrarol21 <- lm(ceftraroline_log2 ~ oxa, data = ceftraroline)   
summary(ceftrarol21)

ceftrarol22 <- lm(ceftraroline_log2 ~ ndm, data = ceftraroline)   
summary(ceftrarol22)

ceftrarol23 <- lm(ceftraroline_log2 ~ imp, data = ceftraroline)   
summary(ceftrarol23)

ceftrarol24 <- lm(ceftraroline_log2 ~ vim, data = ceftraroline)   
summary(ceftrarol24)

ceftrarol25 <- lm(ceftraroline_log2 ~ shv, data = ceftraroline)   
summary(ceftrarol25)

ceftrarol26 <- lm(ceftraroline_log2 ~ tem, data = ceftraroline)   
summary(ceftrarol26)

```


#Multiple liniear Regression_Ceftraroline
```{r}
ceftraroline$bacteria <- relevel(ceftraroline$bacteria, ref = "E. coli")
ceftraroline$Gender <- relevel(ceftraroline$Gender, ref = "Male")



mceftrarol1 <-lm(ceftraroline_log2 ~ Country+bacteria+Gender+Age.Group+Speciality+Year2+ctxm1+ctxm2+ctxm825+ctxm9+veb+per+ges+acc+cmy2+dha+fox+act+kpc+oxa+ndm+imp+vim+shv+tem, data = ceftraroline)


summary(mceftrarol1) #Adjusted R^2 =75%

# Model diagnostics and checking
par(mfrow=c(2,2))
plot(mceftrarol1)

# Extract the residuals
aov_residuals_mceftrarol1 <- residuals(object = mceftrarol1)
# Run Shapiro-Wilk test
#shapiro.test(x = aov_residuals_mceftrarol1)


vif(mceftrarol1)

#Multicollinearity test :There was no collinearity between the variables in model 1 and 2



# Statistical test for constant variance or homoscedasticity
bptest (mceftrarol1)


#p value is less than 0.05 so heterocedasticity present


```



#Robust model_Ceftraroline

```{r}
library(sandwich)
library(lmtest)
mceftrarol1_robust <- coeftest(mceftrarol1, vcov = vcovHC(mceftrarol1, type = "HC1"))
mceftrarol1_robust

confint(mceftrarol1_robust)

#Log back transform was done in log Base 2 calculator
#https://www.omnicalculator.com/math/log-2


```


##Imipenem
```{r}

imipenem1 <-read.csv("imipenem.csv")

imipenem <- imipenem1 %>% 
  filter(Gender %in% c("Male", "Female"), Age.Group %in% c("0 to 2 Years", "3 to 12 Years", "13 to 18 Years", "19 to 64 Years", "65 to 84 Years", "85 and Over"))%>%
  select(bacteria, Country, Gender, Age.Group, Speciality, Year, Imipenem_mic, shv, tem, ctxm1, ctxm2, ctxm825, ctxm9, veb, per, ges, acc, cmy2, dha, fox, act, kpc, oxa, ndm, imp, vim)


str(imipenem)
summary(imipenem)
hist(imipenem$Imipenem_mic)

#log transforma
imipenem$imipenem_log2 <-log2(imipenem$Imipenem_mic)
hist(imipenem$imipenem_log2)


imipenem$bacteria <- as.factor(imipenem$bacteria)
imipenem$Country <- as.factor(imipenem$Country)
imipenem$Gender <- as.factor(imipenem$Gender)
imipenem$Age.Group <- as.factor(imipenem$Age.Group)
imipenem$Speciality <- as.factor(imipenem$Speciality)
imipenem$Year <- as.factor(imipenem$Year)
imipenem$shv <- as.factor(imipenem$shv)
imipenem$tem <- as.factor(imipenem$tem)
imipenem$ctxm1 <- as.factor(imipenem$ctxm1)
imipenem$ctxm2 <- as.factor(imipenem$ctxm2)
imipenem$ctxm825 <- as.factor(imipenem$ctxm825)
imipenem$ctxm9 <- as.factor(imipenem$ctxm9)
imipenem$veb <- as.factor(imipenem$veb)
imipenem$per <- as.factor(imipenem$per)
imipenem$ges <- as.factor(imipenem$ges)
imipenem$acc <- as.factor(imipenem$acc)
imipenem$cmy2 <- as.factor(imipenem$cmy2)
imipenem$dha <- as.factor(imipenem$dha)
imipenem$fox <- as.factor(imipenem$fox)
imipenem$act <- as.factor(imipenem$act)
imipenem$kpc <- as.factor(imipenem$kpc)
imipenem$oxa <- as.factor(imipenem$oxa)
imipenem$ndm <- as.factor(imipenem$ndm)
imipenem$imp <- as.factor(imipenem$imp)
imipenem$vim <- as.factor(imipenem$vim)


imipenem$Year2 <- as.numeric(imipenem$Year)

```


#Simple linear regression_Ceftraroline
```{r}

library(lmtest)

imi1 <- lm(imipenem_log2 ~ bacteria, data = imipenem)   
summary(imi1)

imi2 <- lm(imipenem_log2 ~ Country, data = imipenem)   
summary(imi2)

imi3 <- lm(imipenem_log2 ~ Gender, data = imipenem)   
summary(imi3)

imi4 <- lm(imipenem_log2 ~ Age.Group, data = imipenem)   
summary(imi4)

imi5 <- lm(imipenem_log2 ~ Speciality, data = imipenem)   
summary(imi5)

imi6 <- lm(imipenem_log2 ~ Year2, data = imipenem)   
summary(imi6)

imi7 <- lm(imipenem_log2 ~ ctxm1, data = imipenem)   
summary(imi7)

imi8 <- lm(imipenem_log2 ~ ctxm2, data = imipenem)   
summary(imi8)

imi9 <- lm(imipenem_log2 ~ ctxm825, data = imipenem)   
summary(imi9)

imi10 <- lm(imipenem_log2 ~ ctxm9, data = imipenem)   
summary(imi10)

imi11 <- lm(imipenem_log2 ~ veb, data = imipenem)   
summary(imi11)

imi12 <- lm(imipenem_log2 ~ per, data = imipenem)   
summary(imi12)

imi13 <- lm(imipenem_log2 ~ ges, data = imipenem)   
summary(imi13)

imi14 <- lm(imipenem_log2 ~ acc, data = imipenem)   
summary(imi14)

imi15 <- lm(imipenem_log2 ~ cmy2, data = imipenem)   
summary(imi15)

imi17 <- lm(imipenem_log2 ~ dha, data = imipenem)   
summary(imi17)

imi18 <- lm(imipenem_log2 ~ fox, data = imipenem)   
summary(imi18)

imi19 <- lm(imipenem_log2 ~ act, data = imipenem)   
summary(imi19)

imi20 <- lm(imipenem_log2 ~ kpc, data = imipenem)   
summary(imi20)

imi21 <- lm(imipenem_log2 ~ oxa, data = imipenem)   
summary(imi21)

imi22 <- lm(imipenem_log2 ~ ndm, data = imipenem)   
summary(imi22)

imi23 <- lm(imipenem_log2 ~ imp, data = imipenem)   
summary(imi23)

imi24 <- lm(imipenem_log2 ~ vim, data = imipenem)   
summary(imi24)

imi25 <- lm(imipenem_log2 ~ shv, data = imipenem)   
summary(imi25)

imi26 <- lm(imipenem_log2 ~ tem, data = imipenem)   
summary(imi26)

```

#Multiple liniear Regression_Imipenem
```{r}
imipenem$bacteria <- relevel(imipenem$bacteria, ref = "E. coli")
imipenem$Gender <- relevel(imipenem$Gender, ref = "Male")



mimi1 <-lm(imipenem_log2 ~ Country+bacteria+Gender+Age.Group+Speciality+Year2+ctxm1+ctxm2+ctxm825+ctxm9+veb+per+ges+acc+cmy2+dha+fox+act+kpc+oxa+ndm+imp+vim+shv+tem, data = imipenem)


summary(mimi1) #Adjusted R^2 =76%

# Model diagnostics and checking
par(mfrow=c(2,2))
plot(mimi1)

# Extract the residuals
aov_residuals_mimi1 <- residuals(object = mimi1)
# Run Shapiro-Wilk test
#shapiro.test(x = aov_residuals_mimi1)



vif(mimi1)
#Multicollinearity test :There was no collinearity between the variables in model 1 and 2


# Statistical test for constant variance or homoscedasticity
bptest (mimi1)

#p value is less than 0.05 so heterocedasticity present


```


#Robust model_Imipenem
```{r}
library(sandwich)
library(lmtest)
mimi1_robust <- coeftest(mimi1, vcov = vcovHC(mimi1, type = "HC1"))
mimi1_robust
confint(mimi1_robust)

#Log back transform was done in log Base 2 calculator
#https://www.omnicalculator.com/math/log-2

```



#Meropenem


```{r}
meropenem1 <-read.csv("meropenem.csv")

meropenem1$Meropenem_mic


meropenem <- meropenem1 %>% 
  filter(Gender %in% c("Male", "Female"), Age.Group %in% c("0 to 2 Years", "3 to 12 Years", "13 to 18 Years", "19 to 64 Years", "65 to 84 Years", "85 and Over"))%>%
  select(bacteria, Country, Gender, Age.Group, Speciality, Year, Meropenem_mic, shv, tem, ctxm1, ctxm2, ctxm825, ctxm9, veb, per, ges, acc, cmy2, dha, fox, act, kpc, oxa, ndm, imp, vim)


str(meropenem)
summary(meropenem)
hist(meropenem$Meropenem_mic)

#log transformation
meropenem$meropenem_log2 <-log2(meropenem$Meropenem_mic)
hist(meropenem$meropenem_log2)


meropenem$bacteria <- as.factor(meropenem$bacteria)
meropenem$Country <- as.factor(meropenem$Country)
meropenem$Gender <- as.factor(meropenem$Gender)
meropenem$Age.Group <- as.factor(meropenem$Age.Group)
meropenem$Speciality <- as.factor(meropenem$Speciality)
meropenem$Year <- as.factor(meropenem$Year)
meropenem$shv <- as.factor(meropenem$shv)
meropenem$tem <- as.factor(meropenem$tem)
meropenem$ctxm1 <- as.factor(meropenem$ctxm1)
meropenem$ctxm2 <- as.factor(meropenem$ctxm2)
meropenem$ctxm825 <- as.factor(meropenem$ctxm825)
meropenem$ctxm9 <- as.factor(meropenem$ctxm9)
meropenem$veb <- as.factor(meropenem$veb)
meropenem$per <- as.factor(meropenem$per)
meropenem$ges <- as.factor(meropenem$ges)
meropenem$acc <- as.factor(meropenem$acc)
meropenem$cmy2 <- as.factor(meropenem$cmy2)
meropenem$dha <- as.factor(meropenem$dha)
meropenem$fox <- as.factor(meropenem$fox)
meropenem$act <- as.factor(meropenem$act)
meropenem$kpc <- as.factor(meropenem$kpc)
meropenem$oxa <- as.factor(meropenem$oxa)
meropenem$ndm <- as.factor(meropenem$ndm)
meropenem$imp <- as.factor(meropenem$imp)
meropenem$vim <- as.factor(meropenem$vim)

meropenem$Year2 <- as.numeric(meropenem$Year)

```


#Simple linear regression_Ceftraroline
```{r}

library(lmtest)

mero1 <- lm(meropenem_log2 ~ bacteria, data = meropenem)   
summary(mero1)

mero2 <- lm(meropenem_log2 ~ Country, data = meropenem)   
summary(mero2)

mero3 <- lm(meropenem_log2 ~ Gender, data = meropenem)   
summary(mero3)

mero4 <- lm(meropenem_log2 ~ Age.Group, data = meropenem)   
summary(mero4)

ceftrarol5 <- lm(meropenem_log2 ~ Speciality, data = meropenem)   
summary(ceftrarol5)

ceftrarol6 <- lm(meropenem_log2 ~ Year2, data = meropenem)   
summary(ceftrarol6)

mero7 <- lm(meropenem_log2 ~ ctxm1, data = meropenem)   
summary(mero7)

mero8 <- lm(meropenem_log2 ~ ctxm2, data = meropenem)   
summary(mero8)

mero9 <- lm(meropenem_log2 ~ ctxm825, data = meropenem)   
summary(mero9)

mero10 <- lm(meropenem_log2 ~ ctxm9, data = meropenem)   
summary(mero10)

mero11 <- lm(meropenem_log2 ~ veb, data = meropenem)   
summary(mero11)

mero12 <- lm(meropenem_log2 ~ per, data = meropenem)   
summary(mero12)

mero13 <- lm(meropenem_log2 ~ ges, data = meropenem)   
summary(mero13)

mero14 <- lm(meropenem_log2 ~ acc, data = meropenem)   
summary(mero14)

mero15 <- lm(meropenem_log2 ~ cmy2, data = meropenem)   
summary(mero15)

mero17 <- lm(meropenem_log2 ~ dha, data = meropenem)   
summary(mero17)

mero18 <- lm(meropenem_log2 ~ fox, data = meropenem)   
summary(mero18)

mero19 <- lm(meropenem_log2 ~ act, data = meropenem)   
summary(mero19)

mero20 <- lm(meropenem_log2 ~ kpc, data = meropenem)   
summary(mero20)

mero21 <- lm(meropenem_log2 ~ oxa, data = meropenem)   
summary(mero21)

mero22 <- lm(meropenem_log2 ~ ndm, data = meropenem)   
summary(mero22)

mero23 <- lm(meropenem_log2 ~ imp, data = meropenem)   
summary(mero23)

mero24 <- lm(meropenem_log2 ~ vim, data = meropenem)   
summary(mero24)

mero25 <- lm(meropenem_log2 ~ shv, data = meropenem)   
summary(mero25)

mero26 <- lm(meropenem_log2 ~ tem, data = meropenem)   
summary(mero26)

```


#Multiple liniear Regression_Meropenem
```{r}
meropenem$bacteria <- relevel(meropenem$bacteria, ref = "E. coli")
meropenem$Gender <- relevel(meropenem$Gender, ref = "Male")



mmero1 <-lm(meropenem_log2 ~ Country+bacteria+Gender+Age.Group+Speciality+Year2+ctxm1+ctxm2+ctxm825+ctxm9+veb+per+ges+acc+cmy2+dha+fox+act+kpc+oxa+ndm+imp+vim+shv+tem, data = meropenem)


summary(mmero1)
```

#Robust model_meropenem

```{r}
library(sandwich)
library(lmtest)
mmero1_robust <- coeftest(mmero1, vcov = vcovHC(mmero1, type = "HC1"))
mmero1_robust

confint(mmero1_robust)

#Log back transform was done in log Base 2 calculator
#https://www.omnicalculator.com/math/log-2


```





